One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-11-11 submissions/response_to_reviews_1.md

This paper presents an easy to use software for the One-dimensional
Turbulence (ODT) model that helps to remove the barrier for researchers
wanting to learn about ODT. The code is easy to understand and change to
suit different requirements. The paper is well-written, the software is
carefully explained, and the example provided demonstrates the use of
the software. I recommend publication subject to some minor edits and
clarifications as noted below.

***We appreciate the reviewer's and their careful review of the paper.***

-   Building OPT:

    -   YAML: specify the name of the needed yaml package is: yaml-cpp

    ***We made this clarification in section 2.3.1 as requested.***

@@

-   Input files: Consider adding a feature that helps to specify the
    dumpTimes. For example, add the capability to parse the following
    values (Start, End, Step ) from the input file rather than
    specifying all the times you want to save the data manually.

    ***We have now included this feature as requested. The user can specify times either through the original dumpTimes key, or through a new dumpTimesGen key that includes start, stop, and step variables. If both are present in the input file dumpTimesGen takes precedence, unless a negative start time is specified. This is demonstrated in the newly modified input file for the channel flow case, with comments to note the behavior and usage. We have also edited the paper and code documentation appropriately.

@@

        -   consider using python classes for the interface, it will
            make you code much cleaner

        -   check argparse module in python!

-   Data files and Post-processing:

    -   In the paper, you mentioned in line 118 that the package
        contains auxiliary data processing and visualization tools.
        However, later in section 2.3.4 Data files and post-processing
        you mentioned in line 237 that those tools are organized by case
        type meaning that these post-processing tools are specific for
        the input files provided as examples. This may cause confusion
        to the user.

@@

        -   I recommend that you put these functions under a python
            class that takes as a value the path to the data you saved.
            This will give flexibility to the user to load any data
            stored on his local or remote machines.

        -   Describe those functions in the paper.

    -   Also, I would recommend that the post-processing data examples
        you provided be written in Jupyter notebooks for clarity.

        ***This is a good recommendation. We have included a Jupyter notebook for post-processing the channelFlow, pipeFlow, and laminar_mixing_layer cases, with the latter already present. These will process the data and show comparison plots with the results. The previous stats.py functions are retained for consistency with the demonstration video and the codeocean module. The README files are updated. We have not made a jupyter notebook for the coldJet or jetFlame cases since these are larger simulations that are meant to be run and post-processed on a parallel processor with a job submission script, and that is how we and previous users have interacted with the code.***

### 2020-11-11 submissions/revision_1/manuscript.tex
response updates: response document and manuscript. Corresponding changes made to the code and code documentation.

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{fig_data_folder_structure.pdf} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file. These correspond to the order of the time steps listed in \texttt{input.yaml}.}
\label{fig:data_folder_structure}
\end{figure}

To use post-processing tools, users navigate to the \texttt{post} directory. Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}). Each set of post-processing tools is different, but may contain some combination of Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files. Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.

>>>>

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{fig_data_folder_structure.pdf} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the index of the list of ``dump" times included in, or generated from the information in \texttt{input.yaml}.}
\label{fig:data_folder_structure}
\end{figure}

To use post-processing tools, users navigate to the \texttt{post} directory. Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}). Each set of post-processing tools is different, but may contain some combination of Jupyter notebooks, Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files. Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.
